\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for Marginal Distributions of Stationary Time Series

### 2024-02-29 manuscript/manuscript.tex
removed addressed comments

Let us first consider the case where $X_i$'s are i.i.d. Denote by $F^{(b)}_n$ 
the empirical distribution of the $b$th bootstrap sample and let
$\hat\theta^{(b)}_n$ be the parameter estimate based on the $b$th bootstrap 
sample. 
Using the bootstrap (asymptotic) theory, we can approximate the distribution of
\jy{need references to back up}
$\sqrt{n}(F_n(x) - F(x))$ and $\sqrt{n}(F(x; \hat\theta_n) - F(x))$
by that of $\sqrt{n}(F^{(b)}_n(x) - F_n(x))$
and
$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat\theta_n))$, respectively.
Therefore, if we define
\begin{align*}
Y^{(b)}_n(x) &= \sqrt{n}(F^{(b)}_n(x) - F_n(x)) - 
               \sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat\theta_n)) \\
             &= \sqrt{n}(F^{(b)}_n(x) - F(x; \hat\theta^{(b)}_n)) - 
               \sqrt{n}(F_n(x) - F(x; \hat\theta_n)),
\end{align*}
then $T^{(b)}_n := \sup_x|Y^{(b)}_n(x)|$ is the bootstrap statistic that is 
expected
to approximate the distribution of $T_n$. We note that the term
$\sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is exactly the bias term considered in 
\citet{babu2004goodness}.

@@

In summary, the procedure of the nonparametric block bootstrap test is 
summarized as follows. Repeat the following steps for $b \in \{1, ..., B\}$.
\jy{Whrere is the 'block' part?}
\mc{addressed}
\begin{enumerate}
\item
  Generate $X^{(b)}_1,...,X^{(b)}_n$ by applying moving block bootstrap 
  on the original sample as
  defined previously.
\item
  Fit $F_\theta$ to $X^{(b)}_1,...,X^{(b)}_n$ and obtain estimate 
	$\hat\theta^{(b)}_n$ of $\theta$.
\item
  Obtain the empirical distribution function $F^{(b)}_n$ of
  $X^{(b)}_1,...,X^{(b)}_n$. 
\item
  Calculate bootstrap KS statistic
  \[
    T^{(b)}_n = \sup_x | \sqrt{n}\left(F^{(b)}_n(x) 
    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) |.
  \]
  where 
  $B_{n}(x) = \sqrt{n}(E[F^{(b)}_n(x)] - 
  F(x; E[\hat\theta^{(b)}_n]))$ is the known
  bias term.
\end{enumerate}

@@

\jy{Give details on how the data were generated. Are these enough infomation for
  people reproduce the results? I'd suggest that we use Kendall's tau to measure
  the serial dependence. }

We generated time series with marginal distributions $N(8, 8)$ and
\jy{why choose these two distributions?}\mc{addressed}
$\Gamma(8, 1)$, Kendall's $\tau \in \{-.75, -.5, -.25, 0, .25, .5, 
.75\}$, and
sample size $n \in \{100, 200, 400, 800\}$. Kendall's $\tau$ was chosen as a
measure of serial dependence as it does not vary between two different 
distributions.
The autocorrelation $\phi$ of the series was set to \{-0.924, -0.707, 
-0.383, 0, 0.383, 0.707, 0.924\}. These
are the autocorrelations of the normal series, but after the transformation
to the marginal gamma distribution, the autocorrelations are $\{-0.607, 
diverges,
-0.287, 0, 0.339, 0.668, 0.911\}$.
\mc{my explanation needs work}

@@

\jy{Reduce width of  the panel title section. Reduce the font size of the
  labels. Generate the figures with the right size in mind. Use whole textwidth.}

@@

\jy{Clean up the tables. Use percentage for power. Keep three effective
  digits. Why are there so many decimal places? }
\mc{reduced number of digits}

\jy{The large number decimals in the old table: some numerical issues?}

\jy{Only three sample sizes will be enough. Sample size 800 or higher give
  power~1. Only report nominal size 0.05 would be ok. May consider presenting
  the intervals in a figure.}
\mc{only included three sample sizes and for alpha $=$ 0.05}

@@

\jy{No need for such small a table. Could plot the histogram and fitted density.}

@@

@@

\jy{Normal was not rejected for 1 year. How about 2 year, 3 year, 4 year?}
\mc{tried these sample sizes, normal is rejected for all three might want to
  try 1.5 years}

\jy{I'm surprised that t does not fit well even for two years data.}

>>>>

Let us first consider the case where $X_i$'s are independent. Denote by
$F^{(b)}_n$ the empirical distribution of the $b$th bootstrap sample and let
$\hat\theta^{(b)}_n$ be the parameter estimate based on the $b$th bootstrap 
sample. 
Using the bootstrap (asymptotic) theory, we can approximate the distribution of
$\sqrt{n}(F_n(x) - F(x))$ and $\sqrt{n}(F(x; \hat\theta_n) - F(x))$
by that of $\sqrt{n}(F^{(b)}_n(x) - F_n(x))$ and
$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat\theta_n))$, respectively.
Therefore, if we define
\begin{align*}
Y^{(b)}_n(x) &= \sqrt{n}(F^{(b)}_n(x) - F_n(x)) - 
               \sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat\theta_n)) \\
             &= \sqrt{n}(F^{(b)}_n(x) - F(x; \hat\theta^{(b)}_n)) - 
               \sqrt{n}(F_n(x) - F(x; \hat\theta_n)),
\end{align*}
then $T^{(b)}_n := \sup_x|Y^{(b)}_n(x)|$ is the bootstrap statistic that is 
expected to approximate the distribution of $T_n$. We note that the term
$\sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is exactly the bias term considered in 
\citet{babu2004goodness}.

@@

In summary, the procedure of the nonparametric block bootstrap test is 
summarized as follows. Repeat the following steps for $b \in \{1, ..., B\}$.
\begin{enumerate}
\item
  Generate $X^{(b)}_1,...,X^{(b)}_n$ by applying moving block bootstrap 
  on the original sample as
  defined previously.
\item
  Fit $F_\theta$ to $X^{(b)}_1,...,X^{(b)}_n$ and obtain estimate 
	$\hat\theta^{(b)}_n$ of $\theta$.
\item
  Obtain the empirical distribution function $F^{(b)}_n$ of
  $X^{(b)}_1,...,X^{(b)}_n$. 
\item
  Calculate bootstrap KS statistic
  \[
    T^{(b)}_n = \sup_x | \sqrt{n}\left(F^{(b)}_n(x) 
    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) |.
  \]
  where 
  $B_{n}(x) = \sqrt{n}(E[F^{(b)}_n(x)] - 
  F(x; E[\hat\theta^{(b)}_n]))$ is the known
  bias term.
\end{enumerate}

@@

We generated time series with marginal distributions $N(8, 8)$ and
$\Gamma(8, 1)$, Kendall's
\jy{Need to state how serial dependence were introduced, like you did in the
  first paper: transforming a normal series.}
$\tau \in \{-.75, -.5, -.25, 0, .25, .5, 75\}$, and
sample size $n \in \{100, 200, 400, 800\}$. Kendall's $\tau$ was chosen as a
measure of serial dependence as it does not vary between two different 
distributions.
The autocorrelation $\phi$ of the series was set to
$\{-0.924, -0.707, -0.383, 0, 0.383, 0.707, 0.924\}$. These
are the autocorrelations of the normal series, but after the transformation
to the marginal gamma distribution, the autocorrelations are $\{-0.607, 
diverges, -0.287, 0, 0.339, 0.668, 0.911\}$.
\mc{my explanation needs work}

@@

@@

@@

\jy{Is the parametric method by Zeimberkakis?}

@@

\jy{Sorry I forgot to send you the data I promised. Remind in the future
  please. }

@@
